Quantifying stochastic noise in cultured\\ circadian reporter cells

### 2015-03-13 main_text.tex

\begin{figure}[tbp]
  \begin{center}
    \includegraphics[width=0.8\textwidth]{figures/pdfs/fitted_parameters.pdf}
  \end{center}
  \caption{{\bfseries Distributions in fitted parameters for the genome-wide siRNA screen.} Distributions in robust z-scores closely resemble normal distributions. For all parameters, the region of highest density is consistent between the control and perturbed populations, indicating many perturbations do not appreciably change clock dynamics.} 
\label{fig:fit_distributions}
\end{figure}

@@

\begin{figure}[tbp]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{figures/pdfs/small_molecule_r2.pdf}
  \end{center}
  \caption{{\bfseries Fit quality for the dose-dependent small molecule screens.} The bioluminescence rhythms in both reporter systems were well-described by a damped sinusoid. As the molecules were toxic to the reporter cells at high concentrations, fit quality declined with increasing dosage. Only fits with $R^2 > 0.8$ were kept for further analysis.}
\label{fig:small_molecule_r2}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{figures/pdfs/volume_calibration.pdf}
  \end{center}
  \caption{{\bfseries Calibration curve for fitting the volume parameter to experimental data.} The model's volume parameter was linearly related to the population-averaged damping rate on a log-log scale. Error bars represent the standard error of the mean, calculated by $10$ independent replicates for each volume. Points shown in gray had an average $R^2 < 0.9$ and were excluded from the linear regression. Solid and dashed grey lines indicate the mean and $95\%$ confidence intervals of the linear regression, respectively.}
\label{fig:vol_calibration}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    \includegraphics[width=0.8\textwidth]{figures/pdfs/zhang_plates.pdf}
  \end{center}
  \caption{{\bfseries Plate-to-plate variation of fitted parameters in the Zhang {\itshape et al.,} 2009 genome-wide siRNA screen.} Dots indicate the median of each plate, with lines extending from the $5^\text{th}$ to $95^\text{th}$ percentile. While parameter fits were of similar magnitude for all plates, some inconsistencies were present. In order to accurately compare perturbations and controls between plate experiments, we normalized fitted parameters on a plate-by-plate basis.}
\label{fig:plate_variation}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    \includegraphics[width=0.8\textwidth]{figures/pdfs/zhang_wells.pdf}
  \end{center}
  \caption{{\bfseries Well-to-well variation in the Zhang {\itshape et al.,} 2009 genome-wide siRNA screen.} Similar to Figure~\ref{fig:plate_variation}, dots indicate the median value of each parameter in each well, with lines extending from the $5^\text{th}$ to $95^\text{th}$ percentile. Well position did not seem to affect the fitted values, particularly in the middle regions which contained the siRNA knockdown library. Wells on either end showed significant variation, but these are likely due to the spotting of long- and short-period controls in the same position on each plate.}
\label{fig:well_variation}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    \includegraphics[width=0.7\textwidth]{figures/pdfs/FigS5.pdf}
  \end{center}
  \caption{{\bfseries Variability in period length from cycle to cycle is greater than from cell to cell.} Using single-cell fibroblast data from \cite{Leise2012}, a distribution of period lengths were calculated for each cell. Average period length for each cell is shown by a blue dot, with cells sorted from lowest to highest average period. Error bars extend from the $5^\text{th}$ to $95^\text{th}$ percentile period within each cell. The gray shaded region extends from the $5^\text{th}$ to $95^\text{th}$ percentile of the average period lengths for the entire population. $87\%$ of cells show greater variability from cycle-to-cycle than the overall period heterogeneity.}
  \label{fig:cell2cell-variability}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    \includegraphics[width=0.7\textwidth]{figures/pdfs/FigS6.pdf}
  \end{center}
  \caption{{\bfseries Period heterogeneity and phase diffusion display different damping profiles.} ({\itshape Left}) A simulated population of homogeneous, noisy oscillators dephases due to cycle-to-cycle variability. The envelope of the averaged expression is proportional to $t$.
({\itshape Right}) A deterministic, heterogeneous population dephases due to different free-running periods. In this case, the population displays ballistic phase diffusion, in which envelope of the population-averaged expression changes proportionally to $t^2$.}
  \label{fig:dephasing-rates}
\end{figure}

>>>>

\begin{figure}[tbp]
  \begin{center}
    % \includegraphics[]{figures/pdfs/Fig5.pdf}
  \end{center}
  \caption{{\bfseries Distributions in fitted parameters for the genome-wide siRNA screen.} Distributions in robust z-scores closely resemble normal distributions. For all parameters, the region of highest density is consistent between the control and perturbed populations, indicating many perturbations do not appreciably change clock dynamics.} 
\label{fig:fit_distributions}
\end{figure}

@@

\begin{figure}[tbp]
  \begin{center}
    % \includegraphics[]{figures/pdfs/FigS1.pdf}
  \end{center}
  \caption{{\bfseries Fit quality for the dose-dependent small molecule screens.} The bioluminescence rhythms in both reporter systems were well-described by a damped sinusoid. As the molecules were toxic to the reporter cells at high concentrations, fit quality declined with increasing dosage. Only fits with $R^2 > 0.8$ were kept for further analysis.}
\label{fig:small_molecule_r2}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    % \includegraphics[]{figures/pdfs/FigS2.pdf}
  \end{center}
  \caption{{\bfseries Calibration curve for fitting the volume parameter to experimental data.} The model's volume parameter was linearly related to the population-averaged damping rate on a log-log scale. Error bars represent the standard error of the mean, calculated by $10$ independent replicates for each volume. Points shown in gray had an average $R^2 < 0.9$ and were excluded from the linear regression. Solid and dashed grey lines indicate the mean and $95\%$ confidence intervals of the linear regression, respectively.}
\label{fig:vol_calibration}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    % \includegraphics[]{figures/pdfs/FigS3.pdf}
  \end{center}
  \caption{{\bfseries Plate-to-plate variation of fitted parameters in the Zhang {\itshape et al.,} 2009 genome-wide siRNA screen.} Dots indicate the median of each plate, with lines extending from the $5^\text{th}$ to $95^\text{th}$ percentile. While parameter fits were of similar magnitude for all plates, some inconsistencies were present. In order to accurately compare perturbations and controls between plate experiments, we normalized fitted parameters on a plate-by-plate basis.}
\label{fig:plate_variation}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    % \includegraphics[]{figures/pdfs/FigS4.pdf}
  \end{center}
  \caption{{\bfseries Well-to-well variation in the Zhang {\itshape et al.,} 2009 genome-wide siRNA screen.} Similar to Figure~\ref{fig:plate_variation}, dots indicate the median value of each parameter in each well, with lines extending from the $5^\text{th}$ to $95^\text{th}$ percentile. Well position did not seem to affect the fitted values, particularly in the middle regions which contained the siRNA knockdown library. Wells on either end showed significant variation, but these are likely due to the spotting of long- and short-period controls in the same position on each plate.}
\label{fig:well_variation}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    % \includegraphics[width=0.7\textwidth]{figures/pdfs/FigS5.pdf}
  \end{center}
  \caption{{\bfseries Variability in period length from cycle to cycle is greater than from cell to cell.} Using single-cell fibroblast data from \cite{Leise2012}, a distribution of period lengths were calculated for each cell. Average period length for each cell is shown by a blue dot, with cells sorted from lowest to highest average period. Error bars extend from the $5^\text{th}$ to $95^\text{th}$ percentile period within each cell. The gray shaded region extends from the $5^\text{th}$ to $95^\text{th}$ percentile of the average period lengths for the entire population. $87\%$ of cells show greater variability from cycle-to-cycle than the overall period heterogeneity.}
  \label{fig:cell2cell-variability}
\end{figure}

\begin{figure}[tbp]
  \begin{center}
    % \includegraphics[width=0.7\textwidth]{figures/pdfs/FigS6.pdf}
  \end{center}
  \caption{{\bfseries Period heterogeneity and phase diffusion display different damping profiles.} ({\itshape Left}) A simulated population of homogeneous, noisy oscillators dephases due to cycle-to-cycle variability. The envelope of the averaged expression is proportional to $t$.
({\itshape Right}) A deterministic, heterogeneous population dephases due to different free-running periods. In this case, the population displays ballistic phase diffusion, in which envelope of the population-averaged expression changes proportionally to $t^2$.}
  \label{fig:dephasing-rates}
\end{figure}
